### 2019-06-01 cv/cv-body.tex
Update CV
Fixed name formatting
Add editing/reviewing; remove courses from CV

temperate fire-prone forested region. In press at Ecosphere.

@@

@@

\hypertarget{selected-courses-and-training}{%
\section{Selected courses and
training}\label{selected-courses-and-training}}

\begin{description}
\tightlist
\item[Present]
Proficient in statistical analyses and data management using R, Stan,
JAGS, knitr, Shiny, Git, LaTeX, TMB, SQL.
\item[2016]
Diversity in Conservation Biology, facilitated by Yolanda L. Comedy,
Director of the American Association for the Advancement of Science
(AAAS) Center for Advancing Science \& Engineering Capacity
\item[2015--16]
Powerful Presentation Skills and Media Training with Teresa Erickson and
Tim Ward of Intermedia Communications, authors of
\href{https://www.amazon.com/Master-Communicators-Handbook-Teresa-Erickson/dp/1785351532}{\emph{The
Master Communicator's Handbook}}
\item[2013]
Quantitative Modelling in Ecosystem Based Management. R. Hilborn, School
of Aquatic and Fishery Sciences, University of Washington (audited).
\item[2013]
Applied Time Series Analysis. E. Holmes, M. Scheuerell, and E. Ward;
School of Aquatic and Fishery Sciences, University of Washington
(audited).
\item[2012]
Numerical Computing for the Natural Resources. A.E. Punt, School of
Aquatic and Fishery Sciences, University of Washington (audited).
\item[2012]
Risk Assessment and Decision Analysis for Management of Natural
Resources. R.M. Peterman, School of Resource and Environmental
Management, Simon Fraser University.
\item[2011]
Presenting Data and Information. Edward Tufte, Seattle, WA, United
States.
\end{description}

\hypertarget{reviews}{%
\section{Reviews}\label{reviews}}

Reviewer for Science, Ecology, Ecological Applications, Conservation
Biology, Canadian Journal of Fisheries and Aquatic Sciences, Proceedings
B, Fish and Fisheries, Marine Policy, Population Ecology, Journal of
Applied Ecology, International Journal of Tropical Biology and
Conservation, Journal of Environmental Management, Endangered Species
Research, Aquatic Conservation

>>>>

Beaudreau, A.H., E.J. Ward, R.E. Brenner, A.O. Shelton, J.T. Watson,
J.C. Womack, \textbf{S.C. Anderson}, A.C. Haynie, K.N. Marshall, B.C.
Williams. Thirty years of change and the future of Alaskan fisheries:
Shifts in fishing participation and diversification in response to
environmental, regulatory, and economic pressures. In press at Fish and
Fisheries.

@@

temperate fire-prone forested region. Ecosphere. 10(2):02600.
\url{https://doi.org/10.1002/ecs2.2600}.

@@

\hypertarget{editing-and-reviewing}{%
\section{Editing and Reviewing}\label{editing-and-reviewing}}

\href{https://www.nrcresearchpress.com/page/cjfas/editors}{Associate
Editor} at Canadian Journal of Fisheries and Aquatic Sciences
(2019--present)

\vspace{4mm}

Reviewer for Science, Ecology, Canadian Journal of Fisheries and Aquatic
Sciences, Fish and Fisheries, Ecological Applications, Conservation
Biology, Proceedings B, Marine Policy, Population Ecology, Journal of
Applied Ecology, International Journal of Tropical Biology and
Conservation, Biological Conservation, Oikos, Journal of Environmental
Management, Endangered Species Research, Aquatic Conservation
